---
title: "Incremental Data Room Archive System"
author: "Data Management Team"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    theme: flatly
    code_folding: show
params:
  # Global Configuration
  global_snapshot_id: "2025Q3"
  staging_root: "./temp_staging"  # Temporary staging directory (excluded from git)
  archive_root: "./temp_staging" # Temporary archive root (excluded from git)
  
  # Archive Configurations (can be overridden)
  archive_configs: !r |
    list(
      underwriting = list(
        archive_name = "underwriting",
        source_path = "/mnt/z/Shared/Jaffa Main/Insurance/Reserving and Valuations/Data Room Prep/20250930/Underwriting/TEMP_2025Q3",
        classification_pattern = "^([^/]+)/([^/]+)/",
        exclude_patterns = c("Working Files", "\\.tmp$", "~\\$", "\\.log$")
      # ),
      # claims = list(
      #   archive_name = "claims", 
      #   source_path = "/mnt/z/source/claims/current/",
      #   classification_pattern = "^([^/]+)/([^/]+)/([^/]+)/",
      #   exclude_patterns = c("temp", "backup", "\\.bak$")
      # ),
      # financials = list(
      #   archive_name = "financials",
      #   source_path = "Z:/source/finance/monthly/",
      #   classification_pattern = "^([^/]+)/([^/]+)/",
      #   exclude_patterns = c("draft", "working", "\\.xlsx~$")
      )
    )
  
  # Processing Options
  parallel_processing: true
  create_visualizations: true
  send_notifications: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, 
  warning = FALSE, 
  message = FALSE,
  fig.width = 10,
  fig.height = 6
)

# Load required libraries
library(fs)
library(tidyverse)
library(stringr)
library(lubridate)
library(jsonlite)
library(DT)
library(plotly)
library(knitr)
library(kableExtra)

# Source the generalized functions
source("dataroom_functions.R")
```

# Executive Summary

This report documents the incremental archive process for multiple data room sources as of **`r params$global_snapshot_id`**. The system compares current source files against previous snapshots, identifying new, modified, and unchanged files to create efficient incremental archives.

## Key Features

- **Incremental Processing**: Only new and changed files are copied
- **Metadata Caching**: JSON files store MD5 hashes for fast comparisons
- **Multi-Source Support**: Process multiple archive types simultaneously  
- **Change Tracking**: Detailed logging of what changed and why
- **Reference System**: Unchanged files reference previous snapshots

---

# Configuration

## Global Settings

```{r display-config, results='asis'}
cat("Global Snapshot ID:", params$global_snapshot_id, "\n")
cat("Staging Root:", params$staging_root, "\n")
cat("Archive Root:", params$archive_root, "\n")
cat("Parallel Processing:", params$parallel_processing, "\n")
cat("Number of Archive Sources:", length(params$archive_configs), "\n")
```

## Archive Sources

```{r display-sources}
source_summary <- map_dfr(params$archive_configs, ~ {
  tibble(
    Archive_Name = .x$archive_name,
    Source_Path = .x$source_path,
    Classification_Pattern = .x$classification_pattern,
    Exclusion_Count = length(.x$exclude_patterns)
  )
})

kable(source_summary, caption = "Configured Archive Sources") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

---

# Archive Processing

## Prepare Configurations

```{r prepare-configs}
# Prepare full configurations by adding global settings
full_configs <- map(params$archive_configs, ~ {
  config <- .x
  config$snapshot_id <- params$global_snapshot_id
  config$staging_root <- params$staging_root
  config$archive_root <- params$archive_root  # Don't append archive_name - it's the root for all snapshots
  config
})

# Display prepared configurations
config_df <- map_dfr(full_configs, ~ {
  tibble(
    Archive = .x$archive_name,
    Snapshot_ID = .x$snapshot_id,
    Source = .x$source_path,
    Archive_Root = .x$archive_root,
    Staging_Root = .x$staging_root
  )
})

kable(config_df, caption = "Full Archive Configurations") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  scroll_box(width = "100%")
```

## Execute Archive Process

```{r execute-archives}
start_time <- Sys.time()

# Execute the archive process
if(params$parallel_processing && length(full_configs) > 1) {
  message("Processing archives in parallel...")
  # For now, process sequentially but could be enhanced with future/furrr
  archive_results <- create_multiple_archives(full_configs, params$global_snapshot_id)
} else {
  message("Processing archives sequentially...")
  archive_results <- create_multiple_archives(full_configs, params$global_snapshot_id)
}

end_time <- Sys.time()
processing_time <- end_time - start_time

message("Total processing time: ", round(processing_time, 2), " ", units(processing_time))
```

---

# Results Summary

## Overall Statistics

```{r overall-stats}
summary_stats <- archive_results$summary

stats_df <- tibble(
  Metric = c(
    "Total Archives Processed",
    "Total Files Processed", 
    "Total Files Copied",
    "Total New Files",
    "Total Modified Files",
    "Processing Time"
  ),
  Value = c(
    archive_results$total_archives,
    format(summary_stats$total_files_processed, big.mark = ","),
    format(summary_stats$total_files_copied, big.mark = ","),
    format(summary_stats$total_new_files, big.mark = ","),
    format(summary_stats$total_modified_files, big.mark = ","),
    paste(round(processing_time, 2), units(processing_time))
  )
)

kable(stats_df, caption = "Overall Processing Statistics") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

## Individual Archive Results

```{r individual-results}
individual_stats <- map_dfr(archive_results$individual_results, ~ {
  tibble(
    Archive_Name = .x$archive_config$archive_name,
    Files_New = .x$comparison_summary$new_count,
    Files_Modified = .x$comparison_summary$modified_count,
    Files_Unchanged = .x$comparison_summary$unchanged_count,
    Files_Copied = .x$files_copied,
    Files_Failed = .x$files_failed,
    Status = ifelse(.x$files_failed > 0, "⚠️ With Warnings", "✅ Success")
  )
})

datatable(
  individual_stats,
  caption = "Individual Archive Processing Results",
  options = list(pageLength = 10, autoWidth = TRUE),
  class = "display"
) %>%
  formatStyle(
    "Status",
    backgroundColor = styleEqual("✅ Success", "#d4edda")
  )
```

```{r create-visualizations, eval=params$create_visualizations}
## File Change Distribution

change_data <- individual_stats %>%
  select(Archive_Name, Files_New, Files_Modified, Files_Unchanged) %>%
  pivot_longer(cols = starts_with("Files_"), names_to = "Change_Type", values_to = "Count") %>%
  mutate(Change_Type = str_remove(Change_Type, "Files_"))

# Create interactive bar chart
p1 <- plot_ly(
  change_data,
  x = ~Archive_Name,
  y = ~Count,
  color = ~Change_Type,
  type = "bar",
  colors = c("New" = "#28a745", "Modified" = "#ffc107", "Unchanged" = "#6c757d")
) %>%
  layout(
    title = "File Changes by Archive",
    xaxis = list(title = "Archive"),
    yaxis = list(title = "Number of Files"),
    barmode = "stack"
  )

p1

## Archive Size Distribution

size_data <- map_dfr(archive_results$individual_results, ~ {
  if(file_exists(.x$metadata_file)) {
    metadata <- read_json(.x$metadata_file, simplifyVector = TRUE)
    tibble(
      Archive_Name = .x$archive_config$archive_name,
      Total_Size_MB = round(metadata$summary$total_size / (1024^2), 2),
      File_Count = metadata$summary$total_files
    )
  }
})

if(nrow(size_data) > 0) {
  p2 <- plot_ly(
    size_data,
    x = ~Archive_Name,
    y = ~Total_Size_MB,
    type = "bar",
    marker = list(color = "#007bff")
  ) %>%
    layout(
      title = "Archive Size Distribution",
      xaxis = list(title = "Archive"),
      yaxis = list(title = "Size (MB)")
    )
  
  p2
}
```

---

# Detailed Archive Information

```{r detailed-info, results='asis'}
for(archive_name in names(archive_results$individual_results)) {
  result <- archive_results$individual_results[[archive_name]]
  
  cat("## ", str_to_title(archive_name), " Archive\n\n")
  
  cat("**Configuration:**\n\n")
  cat("- Source Path: ", result$archive_config$source_path, "\n")
  cat("- Staging Path: ", result$staging_path, "\n") 
  cat("- Snapshot ID: ", result$snapshot_id, "\n")
  cat("- Created: ", result$created_at, "\n\n")
  
  cat("**Processing Summary:**\n\n")
  cat("- New Files: ", result$comparison_summary$new_count, "\n")
  cat("- Modified Files: ", result$comparison_summary$modified_count, "\n")
  cat("- Unchanged Files: ", result$comparison_summary$unchanged_count, "\n")
  cat("- Renamed Files: ", result$comparison_summary$renamed_count %||% 0, "\n")
  cat("- Files Copied: ", result$files_copied, "\n")
  cat("- Copy Failures: ", result$files_failed, "\n\n")
  
  # Load and display file summary if available
  summary_file <- path(result$staging_path, paste0(result$snapshot_id, "_file_summary.csv"))
  if(file_exists(summary_file)) {
    file_summary <- read_csv(summary_file, show_col_types = FALSE) %>%
      head(100)  # Limit to first 100 rows for display
    
    if(nrow(file_summary) > 0) {
      cat("**File Summary (First 100 files):**\n\n")
      
      # Create a nice table
      summary_table <- file_summary %>%
        mutate(
          size_mb = round(size / (1024^2), 3),
          modified_date = as.Date(ymd_hms(modified_time))
        ) %>%
        select(Status = status, Category1 = category_1, Category2 = category_2, 
               File = file_name, `Size (MB)` = size_mb, Modified = modified_date) %>%
        arrange(Status, Category1, Category2)
      
      # Print the table with proper markdown formatting
      print(kable(summary_table, caption = paste("File Summary for", str_to_title(archive_name))) %>%
        kable_styling(bootstrap_options = c("striped", "hover", "condensed"), font_size = 10) %>%
        scroll_box(height = "400px"))
    }
  }
  
  cat("\n\n---\n\n")
}
```

---

# Fuzzy Match Suggestions (Rename + Modify Detection)

The system uses intelligent fuzzy matching to identify files that may have been both **renamed AND modified** between snapshots. Since modified files have different MD5 hashes, they would normally appear as separate "REMOVED" and "NEW" files. The fuzzy matcher compares file characteristics (extension, name similarity, size, directory, timestamp) to suggest potential pairs for human review.

```{r fuzzy-match-summary, results='asis'}
# Collect fuzzy match data from all archives
fuzzy_summary <- map_dfr(archive_results$individual_results, ~ {
  result <- .x
  fuzzy_pairs_file <- path(result$staging_path, paste0(result$snapshot_id, "_fuzzy_match_pairs.csv"))
  
  if(file_exists(fuzzy_pairs_file)) {
    pairs <- read_csv(fuzzy_pairs_file, show_col_types = FALSE)
    tibble(
      Archive = result$archive_config$archive_name,
      Total_Pairs = nrow(pairs),
      Flagged_Pairs = sum(pairs$flagged_as_potential, na.rm = TRUE),
      Top_Score = max(pairs$match_confidence_score, na.rm = TRUE)
    )
  } else {
    tibble(
      Archive = result$archive_config$archive_name,
      Total_Pairs = 0,
      Flagged_Pairs = 0,
      Top_Score = NA_real_
    )
  }
})

if(nrow(fuzzy_summary) > 0 && sum(fuzzy_summary$Total_Pairs) > 0) {
  cat("## Summary\n\n")
  cat("Fuzzy matching analyzes removed and new files to identify potential rename-and-modify pairs:\n\n")
  
  kable(fuzzy_summary, 
        caption = "Fuzzy Match Summary by Archive",
        col.names = c("Archive", "Total Pairs Analyzed", "Flagged for Review (≥80)", "Top Score")) %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
  
  cat("\n\n**Scoring Algorithm:**\n\n")
  cat("- **Extension Match**: 25 points (same file type)\n")
  cat("- **Name Similarity**: 30 points (Levenshtein distance)\n")
  cat("- **Size Similarity**: 20 points (within 20% of each other)\n")
  cat("- **Directory Similarity**: 15 points (common path components)\n")
  cat("- **Time Proximity**: 10 points (modified within 30 days)\n")
  cat("- **Threshold**: 80 points (scores ≥80 are flagged for review)\n\n")
  
} else {
  cat("No fuzzy matching data available for this archive period.\n\n")
}
```

```{r fuzzy-flagged-pairs, results='asis'}
# Display flagged pairs for each archive
for(archive_name in names(archive_results$individual_results)) {
  result <- archive_results$individual_results[[archive_name]]
  fuzzy_pairs_file <- path(result$staging_path, paste0(result$snapshot_id, "_fuzzy_match_pairs.csv"))
  
  if(file_exists(fuzzy_pairs_file)) {
    pairs <- read_csv(fuzzy_pairs_file, show_col_types = FALSE)
    flagged_pairs <- pairs %>% filter(flagged_as_potential)
    
    if(nrow(flagged_pairs) > 0) {
      cat("## ", str_to_title(archive_name), " - Flagged Pairs (Score ≥ 80)\n\n")
      cat("⚠️ **", nrow(flagged_pairs), " high-confidence pairs require human review:**\n\n")
      
      # Create detailed table
      flagged_table <- flagged_pairs %>%
        mutate(
          removed_size_mb = round(removed_size / (1024^2), 2),
          new_size_mb = round(new_size / (1024^2), 2),
          size_diff_pct = round(abs(new_size - removed_size) / removed_size * 100, 1)
        ) %>%
        select(
          Score = match_confidence_score,
          `Removed File` = removed_file_name,
          `Removed Size (MB)` = removed_size_mb,
          `Removed Category` = removed_category_1,
          `New File` = new_file_name,
          `New Size (MB)` = new_size_mb,
          `New Category` = new_category_1,
          `Size Δ %` = size_diff_pct
        ) %>%
        arrange(desc(Score))
      
      print(datatable(
        flagged_table,
        caption = paste("High-Confidence Rename+Modify Pairs -", str_to_title(archive_name)),
        options = list(pageLength = 20, autoWidth = TRUE, scrollX = TRUE),
        class = "display compact"
      ) %>%
        formatStyle(
          "Score",
          background = styleColorBar(range(flagged_table$Score), "#28a745"),
          backgroundSize = "100% 90%",
          backgroundRepeat = "no-repeat",
          backgroundPosition = "center"
        ) %>%
        formatRound(c("Score"), 1))
      
      cat("\n\n**Review Guidance:**\n\n")
      cat("1. **Verify each pair** by examining file contents and metadata\n")
      cat("2. **If confirmed as same file**: Mark as RENAMED+MODIFIED (not NEW+REMOVED)\n")
      cat("3. **If different files**: Keep as separate NEW and REMOVED entries\n")
      cat("4. **Check categories**: Files should typically stay in same/related categories\n\n")
      
      cat("---\n\n")
    }
  }
}
```

```{r fuzzy-all-pairs, results='asis'}
# Show all pairs (including below threshold) for manual review
for(archive_name in names(archive_results$individual_results)) {
  result <- archive_results$individual_results[[archive_name]]
  fuzzy_pairs_file <- path(result$staging_path, paste0(result$snapshot_id, "_fuzzy_match_pairs.csv"))
  
  if(file_exists(fuzzy_pairs_file)) {
    pairs <- read_csv(fuzzy_pairs_file, show_col_types = FALSE)
    
    if(nrow(pairs) > 0) {
      cat("## ", str_to_title(archive_name), " - All Suggested Pairs\n\n")
      cat("📊 **Complete fuzzy match analysis** (", nrow(pairs), " pairs analyzed):\n\n")
      cat("*Pairs below threshold (80) are shown for reference but are less likely to be matches.*\n\n")
      
      # Create comprehensive table
      all_pairs_table <- pairs %>%
        mutate(
          removed_size_mb = round(removed_size / (1024^2), 2),
          new_size_mb = round(new_size / (1024^2), 2)
        ) %>%
        select(
          Score = match_confidence_score,
          Flagged = flagged_as_potential,
          `Removed File` = removed_file_name,
          `Removed Category` = removed_category_1,
          `Removed Modified` = removed_modified_time,
          `New File` = new_file_name,
          `New Category` = new_category_1,
          `New Modified` = new_modified_time
        ) %>%
        arrange(desc(Score))
      
      print(datatable(
        all_pairs_table,
        caption = paste("All Fuzzy Match Pairs -", str_to_title(archive_name)),
        options = list(
          pageLength = 10, 
          autoWidth = TRUE, 
          scrollX = TRUE,
          order = list(list(0, 'desc'))  # Sort by score descending
        ),
        class = "display compact",
        filter = 'top'  # Add column filters
      ) %>%
        formatStyle(
          "Flagged",
          backgroundColor = styleEqual(c(TRUE, FALSE), c("#fff3cd", "#ffffff"))
        ) %>%
        formatRound(c("Score"), 1))
      
      cat("\n\n**CSV Export:** Full details available in `", basename(fuzzy_pairs_file), "`\n\n")
      cat("---\n\n")
    }
  }
}
```

---

# File Locations and Next Steps

## Staging Locations

The following staging directories contain the processed files:

```{r staging-locations}
staging_info <- map_dfr(archive_results$individual_results, ~ {
  tibble(
    Archive = .x$archive_config$archive_name,
    Staging_Path = .x$staging_path,
    Metadata_File = .x$metadata_file,
    Files_Ready = file_exists(.x$staging_path)
  )
})

kable(staging_info, caption = "Staging Directory Locations") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  scroll_box(width = "100%")
```

## Manual Steps Required

After reviewing the results above:

1. **Review Staging Areas**: Examine the staging directories to verify the files were processed correctly
2. **Handle Failed Copies**: Check any failed copy logs and resolve issues
3. **Move to Archive**: Copy the staging contents to the final archive locations
4. **Update References**: Update any external systems that reference the archive locations
5. **Cleanup**: Remove staging files after successful archive deployment

## Archive Structure

Each archive follows this structure:
```
{archive_root}/{archive_name}/{snapshot_id}/
├── NEW/                    # New files organized by categories
├── MODIFIED/               # Modified files organized by categories  
├── UNCHANGED/              # Reference information for unchanged files
├── {snapshot_id}_metadata.json          # Complete file metadata
├── {snapshot_id}_archive_report.json    # Processing results
├── {snapshot_id}_file_summary.csv       # Human-readable summary
└── unchanged_file_references.csv        # References to previous snapshots
```

---

# System Health and Recommendations

```{r health-check, results='asis'}
# Check for any issues
issues <- list()

# Check for failed copies
total_failures <- sum(map_dbl(archive_results$individual_results, ~ .x$files_failed))
if(total_failures > 0) {
  issues <- append(issues, paste("⚠️", total_failures, "files failed to copy"))
}

# Check for missing source directories
missing_sources <- map_lgl(full_configs, ~ !dir_exists(.x$source_path))
if(any(missing_sources)) {
  missing_names <- map_chr(full_configs[missing_sources], ~ .x$archive_name)
  issues <- append(issues, paste("⚠️ Missing source directories:", paste(missing_names, collapse = ", ")))
}

# Check staging space
staging_sizes <- map_dbl(archive_results$individual_results, ~ {
  if(dir_exists(.x$staging_path)) {
    sum(file_size(dir_ls(.x$staging_path, recurse = TRUE, type = "file")), na.rm = TRUE)
  } else {
    0
  }
})
total_staging_gb <- sum(staging_sizes) / (1024^3)

if(length(issues) == 0) {
  cat("✅ **System Health: Good**\n\n")
  cat("No critical issues detected.\n\n")
} else {
  cat("⚠️ **System Health: Issues Detected**\n\n")
  for(issue in issues) {
    cat(issue, "\n")
  }
  cat("\n")
}

cat("**Resource Usage:**\n")
cat("- Total staging space used:", round(total_staging_gb, 2), "GB\n")
cat("- Processing time:", round(processing_time, 2), units(processing_time), "\n")
cat("- Memory usage: Check system resources if processing was slow\n\n")

cat("**Recommendations:**\n")
if(total_staging_gb > 10) {
  cat("- Consider cleanup of staging areas after archiving\n")
}
if(as.numeric(processing_time, units = "mins") > 30) {
  cat("- Consider enabling parallel processing for faster execution\n")
}
if(total_failures > 0) {
  cat("- Review failed copy logs and retry failed operations\n")
}
cat("- Schedule regular cleanup of old snapshot metadata files\n")
cat("- Monitor archive storage capacity\n")
```

---

*Report generated on `r Sys.time()` by the Incremental Data Room Archive System*