---
title: "Incremental Data Room Archive System"
author: "Data Management Team"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    theme: flatly
    code_folding: show
params:
  # Global Configuration
  global_snapshot_id: "2025Q2"
  staging_root: "Z:/staging/"
  archive_root: "Z:/archive/"
  
  # Archive Configurations (can be overridden)
  archive_configs: !r list(
    underwriting = list(
      archive_name = "underwriting",
      source_path = "Z:/source/underwriting/2025Q2/",
      classification_pattern = "^([^/]+)/([^/]+)/",
      exclude_patterns = c("Working Files", "\\.tmp$", "~\\$", "\\.log$")
    ),
    claims = list(
      archive_name = "claims", 
      source_path = "Z:/source/claims/current/",
      classification_pattern = "^([^/]+)/([^/]+)/([^/]+)/",
      exclude_patterns = c("temp", "backup", "\\.bak$")
    ),
    financials = list(
      archive_name = "financials",
      source_path = "Z:/source/finance/monthly/",
      classification_pattern = "^([^/]+)/([^/]+)/",
      exclude_patterns = c("draft", "working", "\\.xlsx~$")
    )
  )
  
  # Processing Options
  parallel_processing: true
  create_visualizations: true
  send_notifications: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, 
  warning = FALSE, 
  message = FALSE,
  fig.width = 10,
  fig.height = 6
)

# Load required libraries
library(fs)
library(tidyverse)
library(stringr)
library(lubridate)
library(jsonlite)
library(DT)
library(plotly)
library(knitr)
library(kableExtra)

# Source the generalized functions
source("dataroom_functions.R")
```

# Executive Summary

This report documents the incremental archive process for multiple data room sources as of **`r params$global_snapshot_id`**. The system compares current source files against previous snapshots, identifying new, modified, and unchanged files to create efficient incremental archives.

## Key Features

- **Incremental Processing**: Only new and changed files are copied
- **Metadata Caching**: JSON files store MD5 hashes for fast comparisons
- **Multi-Source Support**: Process multiple archive types simultaneously  
- **Change Tracking**: Detailed logging of what changed and why
- **Reference System**: Unchanged files reference previous snapshots

---

# Configuration

## Global Settings

```{r display-config}
cat("Global Snapshot ID:", params$global_snapshot_id, "\n")
cat("Staging Root:", params$staging_root, "\n")
cat("Archive Root:", params$archive_root, "\n")
cat("Parallel Processing:", params$parallel_processing, "\n")
cat("Number of Archive Sources:", length(params$archive_configs), "\n")
```

## Archive Sources

```{r display-sources}
source_summary <- map_dfr(params$archive_configs, ~ {
  tibble(
    Archive_Name = .x$archive_name,
    Source_Path = .x$source_path,
    Classification_Pattern = .x$classification_pattern,
    Exclusion_Count = length(.x$exclude_patterns)
  )
})

kable(source_summary, caption = "Configured Archive Sources") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

---

# Archive Processing

## Prepare Configurations

```{r prepare-configs}
# Prepare full configurations by adding global settings
full_configs <- map(params$archive_configs, ~ {
  config <- .x
  config$snapshot_id <- params$global_snapshot_id
  config$staging_root <- params$staging_root
  config$archive_root <- path(params$archive_root, config$archive_name)
  config
})

# Display prepared configurations
config_df <- map_dfr(full_configs, ~ {
  tibble(
    Archive = .x$archive_name,
    Snapshot_ID = .x$snapshot_id,
    Source = .x$source_path,
    Archive_Root = .x$archive_root,
    Staging_Root = .x$staging_root
  )
})

kable(config_df, caption = "Full Archive Configurations") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  scroll_box(width = "100%")
```

## Execute Archive Process

```{r execute-archives}
start_time <- Sys.time()

# Execute the archive process
if(params$parallel_processing && length(full_configs) > 1) {
  message("Processing archives in parallel...")
  # For now, process sequentially but could be enhanced with future/furrr
  archive_results <- create_multiple_archives(full_configs, params$global_snapshot_id)
} else {
  message("Processing archives sequentially...")
  archive_results <- create_multiple_archives(full_configs, params$global_snapshot_id)
}

end_time <- Sys.time()
processing_time <- end_time - start_time

message("Total processing time: ", round(processing_time, 2), " ", units(processing_time))
```

---

# Results Summary

## Overall Statistics

```{r overall-stats}
summary_stats <- archive_results$summary

stats_df <- tibble(
  Metric = c(
    "Total Archives Processed",
    "Total Files Processed", 
    "Total Files Copied",
    "Total New Files",
    "Total Modified Files",
    "Processing Time"
  ),
  Value = c(
    archive_results$total_archives,
    format(summary_stats$total_files_processed, big.mark = ","),
    format(summary_stats$total_files_copied, big.mark = ","),
    format(summary_stats$total_new_files, big.mark = ","),
    format(summary_stats$total_modified_files, big.mark = ","),
    paste(round(processing_time, 2), units(processing_time))
  )
)

kable(stats_df, caption = "Overall Processing Statistics") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

## Individual Archive Results

```{r individual-results}
individual_stats <- map_dfr(archive_results$individual_results, ~ {
  tibble(
    Archive_Name = .x$archive_config$archive_name,
    Files_New = .x$comparison_summary$new_count,
    Files_Modified = .x$comparison_summary$modified_count,
    Files_Unchanged = .x$comparison_summary$unchanged_count,
    Files_Copied = .x$files_copied,
    Files_Failed = .x$files_failed,
    Status = ifelse(.x$files_failed > 0, "⚠️ With Warnings", "✅ Success")
  )
})

datatable(
  individual_stats,
  caption = "Individual Archive Processing Results",
  options = list(pageLength = 10, autoWidth = TRUE),
  class = "display"
) %>%
  formatStyle(
    "Status",
    backgroundColor = styleEqual("✅ Success", "#d4edda")
  )
```

```{r create-visualizations, eval=params$create_visualizations}
## File Change Distribution

change_data <- individual_stats %>%
  select(Archive_Name, Files_New, Files_Modified, Files_Unchanged) %>%
  pivot_longer(cols = starts_with("Files_"), names_to = "Change_Type", values_to = "Count") %>%
  mutate(Change_Type = str_remove(Change_Type, "Files_"))

# Create interactive bar chart
p1 <- plot_ly(
  change_data,
  x = ~Archive_Name,
  y = ~Count,
  color = ~Change_Type,
  type = "bar",
  colors = c("New" = "#28a745", "Modified" = "#ffc107", "Unchanged" = "#6c757d")
) %>%
  layout(
    title = "File Changes by Archive",
    xaxis = list(title = "Archive"),
    yaxis = list(title = "Number of Files"),
    barmode = "stack"
  )

p1

## Archive Size Distribution

size_data <- map_dfr(archive_results$individual_results, ~ {
  if(file_exists(.x$metadata_file)) {
    metadata <- read_json(.x$metadata_file, simplifyVector = TRUE)
    tibble(
      Archive_Name = .x$archive_config$archive_name,
      Total_Size_MB = round(metadata$summary$total_size / (1024^2), 2),
      File_Count = metadata$summary$total_files
    )
  }
})

if(nrow(size_data) > 0) {
  p2 <- plot_ly(
    size_data,
    x = ~Archive_Name,
    y = ~Total_Size_MB,
    type = "bar",
    marker = list(color = "#007bff")
  ) %>%
    layout(
      title = "Archive Size Distribution",
      xaxis = list(title = "Archive"),
      yaxis = list(title = "Size (MB)")
    )
  
  p2
}
```

---

# Detailed Archive Information

```{r detailed-info}
for(archive_name in names(archive_results$individual_results)) {
  result <- archive_results$individual_results[[archive_name]]
  
  cat("## ", str_to_title(archive_name), " Archive\n\n")
  
  cat("**Configuration:**\n")
  cat("- Source Path:", result$archive_config$source_path, "\n")
  cat("- Staging Path:", result$staging_path, "\n") 
  cat("- Snapshot ID:", result$snapshot_id, "\n")
  cat("- Created:", result$created_at, "\n\n")
  
  cat("**Processing Summary:**\n")
  cat("- New Files:", result$comparison_summary$new_count, "\n")
  cat("- Modified Files:", result$comparison_summary$modified_count, "\n")
  cat("- Unchanged Files:", result$comparison_summary$unchanged_count, "\n")
  cat("- Renamed Files:", result$comparison_summary$renamed_count %||% 0, "\n")
  cat("- Files Copied:", result$files_copied, "\n")
  cat("- Copy Failures:", result$files_failed, "\n\n")
  
  # Load and display file summary if available
  summary_file <- path(result$staging_path, paste0(result$snapshot_id, "_file_summary.csv"))
  if(file_exists(summary_file)) {
    file_summary <- read_csv(summary_file, show_col_types = FALSE) %>%
      head(100)  # Limit to first 100 rows for display
    
    if(nrow(file_summary) > 0) {
      cat("**File Summary (First 100 files):**\n\n")
      
      # Create a nice table
      summary_table <- file_summary %>%
        mutate(
          size_mb = round(size / (1024^2), 3),
          modified_date = as.Date(ymd_hms(modified_time))
        ) %>%
        select(Status = status, Category1 = category_1, Category2 = category_2, 
               File = file_name, `Size (MB)` = size_mb, Modified = modified_date) %>%
        arrange(Status, Category1, Category2)
      
      print(kable(summary_table, caption = paste("File Summary for", str_to_title(archive_name))) %>%
        kable_styling(bootstrap_options = c("striped", "hover", "condensed"), font_size = 10) %>%
        scroll_box(height = "400px"))
    }
  }
  
  cat("\n---\n\n")
}
```

# File Locations and Next Steps

## Staging Locations

The following staging directories contain the processed files:

```{r staging-locations}
staging_info <- map_dfr(archive_results$individual_results, ~ {
  tibble(
    Archive = .x$archive_config$archive_name,
    Staging_Path = .x$staging_path,
    Metadata_File = .x$metadata_file,
    Files_Ready = file_exists(.x$staging_path)
  )
})

kable(staging_info, caption = "Staging Directory Locations") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed")) %>%
  scroll_box(width = "100%")
```

## Manual Steps Required

After reviewing the results above:

1. **Review Staging Areas**: Examine the staging directories to verify the files were processed correctly
2. **Handle Failed Copies**: Check any failed copy logs and resolve issues
3. **Move to Archive**: Copy the staging contents to the final archive locations
4. **Update References**: Update any external systems that reference the archive locations
5. **Cleanup**: Remove staging files after successful archive deployment

## Archive Structure

Each archive follows this structure:
```
{archive_root}/{archive_name}/{snapshot_id}/
├── NEW/                    # New files organized by categories
├── MODIFIED/               # Modified files organized by categories  
├── UNCHANGED/              # Reference information for unchanged files
├── {snapshot_id}_metadata.json          # Complete file metadata
├── {snapshot_id}_archive_report.json    # Processing results
├── {snapshot_id}_file_summary.csv       # Human-readable summary
└── unchanged_file_references.csv        # References to previous snapshots
```

---

# System Health and Recommendations

```{r health-check}
# Check for any issues
issues <- list()

# Check for failed copies
total_failures <- sum(map_dbl(archive_results$individual_results, ~ .x$files_failed))
if(total_failures > 0) {
  issues <- append(issues, paste("⚠️", total_failures, "files failed to copy"))
}

# Check for missing source directories
missing_sources <- map_lgl(full_configs, ~ !dir_exists(.x$source_path))
if(any(missing_sources)) {
  missing_names <- map_chr(full_configs[missing_sources], ~ .x$archive_name)
  issues <- append(issues, paste("⚠️ Missing source directories:", paste(missing_names, collapse = ", ")))
}

# Check staging space
staging_sizes <- map_dbl(archive_results$individual_results, ~ {
  if(dir_exists(.x$staging_path)) {
    sum(file_size(dir_ls(.x$staging_path, recurse = TRUE, type = "file")), na.rm = TRUE)
  } else {
    0
  }
})
total_staging_gb <- sum(staging_sizes) / (1024^3)

if(length(issues) == 0) {
  cat("✅ **System Health: Good**\n\n")
  cat("No critical issues detected.\n\n")
} else {
  cat("⚠️ **System Health: Issues Detected**\n\n")
  for(issue in issues) {
    cat(issue, "\n")
  }
  cat("\n")
}

cat("**Resource Usage:**\n")
cat("- Total staging space used:", round(total_staging_gb, 2), "GB\n")
cat("- Processing time:", round(processing_time, 2), units(processing_time), "\n")
cat("- Memory usage: Check system resources if processing was slow\n\n")

cat("**Recommendations:**\n")
if(total_staging_gb > 10) {
  cat("- Consider cleanup of staging areas after archiving\n")
}
if(as.numeric(processing_time, units = "mins") > 30) {
  cat("- Consider enabling parallel processing for faster execution\n")
}
if(total_failures > 0) {
  cat("- Review failed copy logs and retry failed operations\n")
}
cat("- Schedule regular cleanup of old snapshot metadata files\n")
cat("- Monitor archive storage capacity\n")
```

---

*Report generated on `r Sys.time()` by the Incremental Data Room Archive System*