---
title: "U/W Folder Data Room Archive"
author: "Chris Laws"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
params:
  current_period: "2025Q2"
  run_staging_directory: "Z:/Shared/Jaffa Main/Insurance/Reserving and Valuations/20250630/Huggins Dataroom/Underwriting/RunLogs/2025Q2/"
  output_staging_directory: "Z:/Shared/Jaffa Main/Insurance/Reserving and Valuations/20250630/Huggins Dataroom/Underwriting/Content/2025Q2/"
  source_directory: "Z:/Shared/Jaffa Main/Insurance/Reserving and Valuations/20250630/Huggins Dataroom/Underwriting/TEMP_2025Q2/"
  archive_directory: "Z:/Shared/Jaffa External/Huggins/Underwriting/Content/"
  archive_staging_directory: "Z:/Shared/Jaffa Main/Insurance/Reserving and Valuations/20250630/Huggins Dataroom/Underwriting/Content/"
  remove_working_files: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Overview

## Purpose
This script was created to incrementally archive U/W source files in the external data room.

U/W source files generally do not change once they are finalized.
And so the script builds a view of the the U/W source files by:
 1. Referencing files already in the archive
 2. Adding new files to the archive
 3. Coping any modified files into the archive.
The script looks to help focus the archive user toward new/modified files while providing easy access to previously existing files.

## Approach
The script compares the current set of U/W source files to those already in the archive.
If the (relative) path, file name, last write time, and size already exist in the archive; the file is assumed unchanged.
Otherwise, the file is assumed to be new/modified and archived file (and associated files) are considered invalid and the current files are added to the archive.

In the event that the file may have existed before, the script tries to summarize what may have changed.
* The script tries to identify files that have the same (relative) path and name, but may have been modified because the last write time and size have changed.
* The script tries to identify files that may have been renamed by first comparing the (relative) path, last write time, and size.
   - If these qualities match, a full file hash is pulled and compared to ensure the contents are consistent between the two files with different names.
   
## Helpful Conventions
- The script associates each collection of files by "segment" and "deal".
- The script assumes that files are stored in a hierarchical file path with a "./<segment>/<deal>/*" convention.
- The script *does not* look for files that have been removed. For instance, is the archive has file XYZ.csv associated with Segment A Deal 1 and the current U/W sources files have removed XYZ.csv, file XYZ.csv will not be considered when comparing the current and archived versions of Segment A Deal 1.

The archive structure should consist of:
1. A Content folder that houses the archived U/W source files. 
   - The Content folder consists of a series of sub-folders.
   - Each sub-folder is typically named in a {YYYY}Q{Q} pattern (e.g., 2025Q2) that corresponds the period in which the files were added.
   - The names *must* sort in R such that max{sub-folder-name} is the most recent.
2. A RunLogs folder the houses the script, logs, intermediate files, etc. used.
   - The Content folder consists of a series of sub-folders.
   - Each sub-folder is typically named in a {YYYY}Q{Q} pattern that corresponds the period in which the files were added.
3. A series of archive directory files.
   - Each archive directory file is typically named in a {YYYY}Q{Q}_Directory.csv pattern that corresponds the period in which the files were added.
 
Note that we used powershell to get this info to avoid a max file path limitation of R packages.
   
## Output
The script output is:
1. A "NEW" folder that contains all "segment"x"deal"(s) that did not previously exist in the archive.
2. A "MOD" folder that contains all "segment"x"deal"(s) that previously existed in the archive but now have files that did not match the archive.
3. An archive directory that includes the full set of "segment"x"deal"s and helpful information such as where to locate the current archived copy and a summary of what may have changed for "segment"x"deal"s showing modified files.

Note that two File Directories are created.
One that references the path relative to the archive staging area; this directory is useful to inspect the output *before* the output is copied into the final archive area.
The other that references the path relative to the final archive area; this directory is useful to navigate the final archive area.

## Running the Script

### Step 1
Setup the new staging area/folder structure.
This can be any new/unused folder. 
Intermediate files, the script, and output will be initially populated into this staging area.
The script should be copied into this new staging folder.

### Step 2
Adjust the values in the YAML parameters section at the top of this document, or pass them when rendering the document.

### Step 3
Compile a Report of the script.
(Ctrl-Shift-K in R Studio or use `rmarkdown::render()`)
The script will deposit the intermediate files, the script, and output into this staging area.

### Step 4
After the staging area has been manually reviewed, the contents can be manually moved into the archive.
The NEW and MOD folders in the staging area should be copied into a newly created {YYYY}Q{Q} sub-folder of the Content folder.
The other files should be copied into a newly created {YYYY}Q{Q} sub-folder of the RunLogs folder.
The archive directory file should copied into the root of the archive (i.e., the same level as the Content and RunLogs folder).

# Input Parameters

The following parameters are configured for this run:

```{r display-params}
# Display current parameters
cat("Current Period:", params$current_period, "\n")
cat("Run Staging Directory:", params$run_staging_directory, "\n") 
cat("Output Staging Directory:", params$output_staging_directory, "\n")
cat("Source Directory:", params$source_directory, "\n")
cat("Archive Directory:", params$archive_directory, "\n")
cat("Archive Staging Directory:", params$archive_staging_directory, "\n")
cat("Remove Working Files:", params$remove_working_files, "\n")
```

# Initialize R

```{r initialize}
R.version
Sys.time()

# Source the underwriting functions
source("underwriting_functions.R")
```

# Execute Archive Process

```{r execute-archive}
# Execute the main archiving function with parameters
result <- archive_underwriting_files(
  current_period = params$current_period,
  run_staging_directory = params$run_staging_directory,
  output_staging_directory = params$output_staging_directory,
  source_directory = params$source_directory,
  archive_directory = params$archive_directory,
  archive_staging_directory = params$archive_staging_directory,
  remove_working_files = params$remove_working_files
)
```

# Summary Results

```{r summary}
cat("Archive process completed successfully!\n")
cat("Current Period:", result$current_period, "\n")
cat("New Deals Found:", nrow(result$new_deals), "\n")
cat("Modified Deals Found:", nrow(result$mod_deals), "\n")
cat("Old Deals (Unchanged):", nrow(result$old_deals), "\n")
cat("Total Files Copied:", result$files_copied, "\n")

if(nrow(result$new_deals) > 0) {
  cat("\nNew Deals:\n")
  print(result$new_deals)
}

if(nrow(result$mod_deals) > 0) {
  cat("\nModified Deals:\n")
  print(result$mod_deals %>% select(segment, deal, n_mod_or_add_files))
}
```

# File Operations Log

The script has created the following outputs in the staging directory:

- `{params$current_period}_Staging_Directory.csv`: Directory file for staging area navigation
- `{params$current_period}_Directory.csv`: Directory file for final archive navigation  
- `NEW/` folder: Contains newly archived segment/deal combinations
- `MOD/` folder: Contains modified segment/deal combinations
- Various intermediate files (`RAW_INFO_*.txt`, `hash.txt`, etc.)

## Next Steps

1. **Review**: Examine the staging area outputs to verify correctness
2. **Move NEW and MOD folders**: Copy to `{archive_directory}/{params$current_period}/`
3. **Move intermediate files**: Copy to RunLogs folder structure
4. **Update archive directory**: Copy the directory CSV to the archive root

---

*End of Report*