---
title: "Data Room Archive Configuration Guide"
author: "External Data Room R Lang Project"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: 
      collapsed: false
      smooth_scroll: true
    theme: flatly
    highlight: tango
    code_folding: show
  pdf_document:
    toc: true
    toc_depth: 3
params:
  show_examples: true
  demo_mode: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE, 
  warning = FALSE, 
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)

# Load required libraries
library(knitr)
library(DT)
library(dplyr)
library(purrr)

# Source the main functions if available
if(file.exists("../dataroom_functions.R")) {
  source("../dataroom_functions.R")
}
```

# Overview

This guide provides comprehensive documentation for configuring the **Data Room Archive System**, a powerful R-based solution for creating incremental backups and managing file archives across multiple business areas.

## Key Features

- **Incremental Processing**: Only copies new or modified files
- **JSON Metadata Caching**: Fast comparisons using MD5 hashes
- **Multi-Source Support**: Process multiple archives simultaneously  
- **Flexible Classification**: Custom regex patterns for folder structures
- **Performance Optimization**: Parallel processing and batch operations
- **Cross-Platform**: Works on Windows, Linux, and WSL

---

# Configuration Basics

## Core Configuration Structure

Every archive configuration requires these essential elements:

```{r config-structure, eval=FALSE}
config <- list(
  archive_name = "your_archive_name",        # Unique identifier
  source_path = "/path/to/source/",          # Where files come from
  archive_root = "/path/to/archive/",        # Where archives are stored
  staging_root = "/path/to/staging/",        # Temporary processing area
  classification_pattern = "regex_pattern",  # How to organize files
  exclude_patterns = c("pattern1", "pattern2") # Files to skip
)
```

## Path Configuration

### Windows Paths
```{r windows-paths, eval=FALSE}
source_path = "Z:/source/underwriting/current/"
archive_root = "Z:/archive/underwriting/"
staging_root = "Z:/staging/"
```

### WSL/Linux Paths  
```{r wsl-paths, eval=FALSE}
source_path = "/mnt/z/source/underwriting/current/"
archive_root = "/mnt/z/archive/underwriting/"
staging_root = "/mnt/z/staging/"
```

---

# Classification Patterns

Classification patterns determine how files are organized in the archive. They use regular expressions with capture groups.

## Common Patterns

### Two-Level Hierarchy (Segment/Deal)
```{r pattern-two-level, eval=FALSE}
classification_pattern = "^([^/]+)/([^/]+)/"
# Matches: SegmentA/Deal123/file.pdf → Groups: ["SegmentA", "Deal123"]
```

### Three-Level Hierarchy (Year/Month/Type)
```{r pattern-three-level, eval=FALSE}
classification_pattern = "^([0-9]{4})/([0-9]{2})/([^/]+)/"
# Matches: 2025/03/Claims/file.xlsx → Groups: ["2025", "03", "Claims"]
```

### Date-Based Pattern
```{r pattern-date, eval=FALSE}
classification_pattern = "^([^/]+)/([^/]+)/([0-9]{4}-[0-9]{2}-[0-9]{2})/"
# Matches: ClientA/Service/2025-03-15/file.doc → Groups: ["ClientA", "Service", "2025-03-15"]
```

### Complex Business Pattern
```{r pattern-complex, eval=FALSE}
classification_pattern = "^([^/]+)/([0-9]{4}Q[1-4])/([^/]+)/"
# Matches: Finance/2025Q1/Reports/file.xlsx → Groups: ["Finance", "2025Q1", "Reports"]
```

## Pattern Testing

```{r pattern-testing, eval=params$show_examples}
# Example: Test a classification pattern
test_pattern <- "^([^/]+)/([0-9]{4}Q[1-4])/"
test_paths <- c(
  "Finance/2025Q1/report.xlsx",
  "Legal/2025Q2/contract.pdf", 
  "Invalid/NotAQuarter/file.txt"
)

# Test the pattern
results <- data.frame(
  path = test_paths,
  matches = grepl(test_pattern, test_paths),
  groups = ifelse(
    grepl(test_pattern, test_paths),
    gsub(test_pattern, "\\1, \\2", test_paths),
    "No match"
  )
)

kable(results, caption = "Pattern Testing Results")
```

---

# Practical Examples

## Example 1: Simple Underwriting Archive

This is the most basic configuration for underwriting files organized by segment and deal:

```{r example-basic, eval=FALSE}
# Load the functions
source("../dataroom_functions.R")

# Basic underwriting configuration  
underwriting_config <- list(
  archive_name = "underwriting",
  snapshot_id = "2025Q4",
  source_path = "/mnt/z/source/underwriting/current/",
  archive_root = "/mnt/z/archive/underwriting/",
  staging_root = "/mnt/z/staging/",
  classification_pattern = "^([^/]+)/([^/]+)/",
  exclude_patterns = c("Working Files", "backup", "\\.tmp$")
)

# Execute the archive
result <- create_incremental_archive(underwriting_config)
```

## Example 2: Multi-Business Area Setup

For organizations with multiple business areas that need separate archives:

```{r example-multi, eval=FALSE}
# Multi-archive configuration
multi_config <- list(
  underwriting = list(
    archive_name = "underwriting",
    source_path = "/mnt/z/source/underwriting/current/",
    classification_pattern = "^([^/]+)/([^/]+)/",
    exclude_patterns = c("Working Files", "backup", "\\.tmp$")
  ),
  
  claims = list(
    archive_name = "claims", 
    source_path = "/mnt/z/source/claims/processed/",
    classification_pattern = "^([0-9]{4})/([0-9]{2})/([^/]+)/",
    exclude_patterns = c("temp", "draft", "\\.bak$")
  ),
  
  financials = list(
    archive_name = "financials",
    source_path = "/mnt/z/source/finance/reports/",
    classification_pattern = "^([^/]+)/([0-9]{4}Q[1-4])/",
    exclude_patterns = c("working", "draft", "\\.xlsx~$")
  )
)

# Global settings
global_snapshot_id <- "2025Q4"
archive_root <- "/mnt/z/archive/"
staging_root <- "/mnt/z/staging/"

# Execute all archives
results <- create_multiple_archives(multi_config, global_snapshot_id)
```

## Example 3: High-Performance Configuration

For large datasets requiring optimization:

```{r example-performance, eval=FALSE}
# Load performance functions
source("../performance_functions.R")

# High-performance configuration
large_scale_config <- list(
  archive_name = "enterprise_data",
  snapshot_id = "2025Q4", 
  source_path = "/mnt/z/source/enterprise/",
  archive_root = "/mnt/z/archive/enterprise/",
  staging_root = "/mnt/z/staging/",
  classification_pattern = "^([^/]+)/([^/]+)/([^/]+)/",
  exclude_patterns = c(
    "Working Files", "temp", "backup", "cache",
    "\\.tmp$", "\\.bak$", "\\.log$", "~\\$.*"
  ),
  
  # Performance settings
  use_parallel_processing = TRUE,
  max_workers = 6,
  batch_size = 100,
  quick_comparison_mode = FALSE,
  enable_cache_management = TRUE,
  max_cache_age_days = 30
)

# Execute with timing
start_time <- Sys.time()
result <- create_incremental_archive(large_scale_config)
end_time <- Sys.time()

cat("Processing completed in:", round(end_time - start_time, 2), "minutes\n")
```

---

# Advanced Configuration Options

## Exclude Patterns

Exclude patterns use regular expressions to skip unwanted files:

```{r exclude-patterns-table, echo=FALSE}
exclude_examples <- data.frame(
  Pattern = c(
    "\\\\.tmp$",
    "\\\\.bak$", 
    "Working Files",
    "~\\\\$.*",
    "thumbs\\\\.db",
    "backup",
    "^temp"
  ),
  Description = c(
    "Files ending in .tmp",
    "Backup files ending in .bak",
    "Folders named 'Working Files'", 
    "Excel temporary files (~$filename)",
    "Windows thumbnail cache files",
    "Any folder named 'backup'",
    "Files/folders starting with 'temp'"
  ),
  Example = c(
    "document.tmp",
    "data.bak",
    "Working Files/draft.docx", 
    "~$spreadsheet.xlsx",
    "thumbs.db",
    "backup/old_file.pdf",
    "temp_analysis.xlsx"
  )
)

kable(exclude_examples, caption = "Common Exclude Patterns")
```

## Performance Settings

```{r performance-settings-table, echo=FALSE}
performance_options <- data.frame(
  Setting = c(
    "use_parallel_processing",
    "max_workers",
    "batch_size", 
    "quick_comparison_mode",
    "enable_cache_management",
    "max_cache_age_days"
  ),
  Type = c("logical", "integer", "integer", "logical", "logical", "integer"),
  Default = c("FALSE", "4", "50", "TRUE", "FALSE", "7"),
  Description = c(
    "Enable parallel file processing",
    "Number of worker processes", 
    "Files processed per batch",
    "Use file size/date vs full hash comparison",
    "Automatically clean old cache files",
    "Days to keep cache files"
  )
)

kable(performance_options, caption = "Performance Configuration Options")
```

---

# Automation and Scheduling

## Scheduled Automation Function

```{r automation-example, eval=FALSE}
# Automated archive with error handling
automated_archive <- function(config_file = "archive_config.json") {
  tryCatch({
    # Load configuration
    configs <- jsonlite::read_json(config_file, simplifyVector = TRUE)
    
    # Generate snapshot ID
    snapshot_id <- paste0(year(Sys.Date()), "Q", quarter(Sys.Date()))
    
    # Create log file
    log_file <- file.path("logs", paste0("archive_", snapshot_id, "_", 
                                        format(Sys.time(), "%Y%m%d_%H%M%S"), ".log"))
    dir.create("logs", showWarnings = FALSE)
    
    # Execute archives
    results <- create_multiple_archives(configs, snapshot_id)
    
    return(results)
    
  }, error = function(e) {
    message("Archive process failed: ", e$message)
    stop(e)
  })
}
```

## Configuration File Format

Save configurations as JSON for automated processing:

```{r json-config, eval=FALSE}
# Create JSON configuration
config_json <- list(
  underwriting = list(
    archive_name = "underwriting",
    source_path = "/mnt/z/source/underwriting/current/",
    archive_root = "/mnt/z/archive/underwriting/", 
    staging_root = "/mnt/z/staging/",
    classification_pattern = "^([^/]+)/([^/]+)/",
    exclude_patterns = c("Working Files", "\\.tmp$")
  )
)

# Save to file
jsonlite::write_json(config_json, "archive_config.json", 
                    pretty = TRUE, auto_unbox = TRUE)
```

---

# Testing and Development

## Development Configuration

For testing with smaller datasets:

```{r dev-config, eval=FALSE}
# Development/testing configuration
dev_config <- list(
  test_archive = list(
    archive_name = "test_data",
    source_path = "/tmp/test_source/",
    archive_root = "/tmp/test_archive/",
    staging_root = "/tmp/test_staging/",
    classification_pattern = "^([^/]+)/([^/]+)/",
    exclude_patterns = c("test_*", "\\.tmp$"),
    
    # Development settings
    max_files_per_category = 100,
    dry_run = FALSE,
    verbose_logging = TRUE
  )
)
```

## Test Validation Function

```{r validation-function, eval=FALSE}
# Validate archive results
validate_archive_results <- function(result) {
  checks <- list(
    metadata_exists = file.exists(result$metadata_file),
    staging_exists = dir.exists(result$staging_path),
    no_copy_failures = result$files_failed == 0,
    reasonable_file_count = result$files_copied >= 0 && result$files_copied <= 1000
  )
  
  list(
    checks = unlist(checks),
    failures = names(checks)[!unlist(checks)]
  )
}
```

---

# Troubleshooting

## Common Issues

### Path Problems
- **Windows vs WSL**: Convert `Z:/` to `/mnt/z/`
- **Trailing Slashes**: Always include trailing slashes in directory paths
- **Permissions**: Ensure R has read/write access to all paths

### Pattern Issues  
- **Escaping**: Use `\\\\` for literal backslashes in R strings
- **Testing**: Test patterns with small datasets first
- **Capture Groups**: Ensure patterns have proper capture groups `()`

### Performance Issues
- **Large Datasets**: Enable parallel processing
- **Network Drives**: Consider local staging areas
- **Memory Usage**: Use batch processing for very large archives

## Debugging Tips

```{r debugging, eval=FALSE}
# Enable verbose logging
options(dataroom.verbose = TRUE)

# Test classification patterns
test_paths <- list.files(source_path, recursive = TRUE, full.names = TRUE)
sample_paths <- head(test_paths, 10)
matches <- str_match(sample_paths, classification_pattern)
print(matches)

# Check file permissions
file.info(source_path)$mode
file.access(archive_root, 2)  # Check write access
```

---

# Integration Examples

## SharePoint Integration

```{r sharepoint-integration, eval=FALSE}
# Upload metadata to SharePoint after archiving
upload_to_sharepoint <- function(metadata_file, archive_name, snapshot_id) {
  # Implementation depends on your SharePoint setup
  message("Uploading metadata for: ", archive_name, " - ", snapshot_id)
}
```

## Database Logging

```{r database-logging, eval=FALSE}
# Log archive events to database
log_to_database <- function(event_type, snapshot_id, timestamp, 
                           archive_name = NULL, files_copied = NULL) {
  # Implementation depends on your database setup
  message("Database log: ", event_type, " - ", snapshot_id)
}
```

## Notification System

```{r notification-system, eval=FALSE}
# Send Teams notification
send_teams_notification <- function(message) {
  # Implement Teams webhook notification
  message("Teams notification: ", message)
}
```

---

# Conclusion

The Data Room Archive System provides a flexible, scalable solution for managing file archives across multiple business areas. Key benefits include:

- **Efficiency**: Incremental processing saves time and storage
- **Reliability**: Comprehensive error handling and validation
- **Flexibility**: Customizable patterns and configurations  
- **Performance**: Parallel processing and optimization options
- **Integration**: APIs for external systems and automation

For additional support, refer to the main project documentation or the `examples/README.md` file.

---

## Session Information

```{r session-info}
sessionInfo()
```